---
title: "Étude de cas 1"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Needed libraries
library("FactoMineR",lib.loc="~/anaconda3/envs/tried/lib/R/library")
library("factoextra", lib.loc="~/anaconda3/envs/tried/lib/R/library")
library("olsrr", lib.loc="~/anaconda3/envs/tried/lib/R/library")
library("e1071", lib.loc="~/anaconda3/envs/tried/lib/R/library")
library("Metrics", lib.loc="~/anaconda3/envs/tried/lib/R/library")
library("caret", lib.loc="~/anaconda3/envs/tried/lib/R/library")

```


```{r, include=TRUE}
Quali <- read.delim("~/Bureau/Etude de cas 1/donnees/CNL_Qualitatives_No_NAN.xls")
Quanti<- read.delim("~/Bureau/Etude de cas 1/donnees/CNL_Quantitatives_No_NAN.xls")
Polluant <- read.delim("~/Bureau/Etude de cas 1/donnees/Polluant-5.txt")
```


```{r}
#types TRANSFORMATION


for (i in 1:length(Quanti$MATER2)){
   if (Quanti$MATER2[i]==1){
     Quanti$MATER2[i]<-"mur_1matos"
   }
  else {
    if (Quanti$MATER2[i]==2){
     Quanti$MATER2[i]<-"mur_2matos"
    }
    else {
      Quanti$MATER2[i]<-"mur_3matos"
    }
  }
}
Quanti$MATER2 <-NULL
Quanti$NPVe1 <- NULL
Quanti$HSRF <- NULL

logement_Quanti <- Quanti[,c(2:31)]




```

```{r, include=TRUE}
for (i in 1:length(Quali$ACTP1)){
   if (Quali$ACTP1[i]==1){
     Quali$ACTP1[i]<-"acti_pro"
   }
  else {
    Quali$ACTP1[i]<-"no_acti_pro"
  }
}
for (i in 1:length(Quali$CHEM1)){
   if (Quali$CHEM1[i]==1){
     Quali$CHEM1[i]<-"avec_chem"
   }
  else {
    Quali$CHEM1[i]<-"sans_chem"
  }
}
for (i in 1:length(Quali$DBRI)){
   if (Quali$DBRI[i]==1){
     Quali$DBRI[i]<-"lieu_brico_coller"
   }
  else {
    if (Quali$DBRI[i]==2){
     Quali$DBRI[i]<-"lieu_brico_non_coller"
    }
    else {
      Quali$DBRI[i]<-"sans_lieu_brico_coller"
    }
  }
}
for (i in 1:length(Quali$DCA3e1)){
   if (Quali$DCA3e1[i]==1){
     Quali$DCA3e1[i]<-"cave_comm"
   }
  else {
    if (Quali$DCA3e1[i]==2){
     Quali$DCA3e1[i]<-"cave_non_comm"
    }
    else {
      Quali$DCA3e1[i]<-"sans_cave"
    }
  }
}

for (i in 1:length(Quali$DGG2be1)){
   if (Quali$DGG2be1[i]==1){
     Quali$DGG2be1[i]<-"garage_attenant"
   }
  else {
    if (Quali$DGG2be1[i]==2){
     Quali$DGG2be1[i]<-"garage_non_attenant"
    }
    else {
      Quali$DGG2be1[i]<-"sans_garage"
    }
  }
}

for (i in 1:length(Quali$FC316)){
   if (Quali$FC316[i]==1){
     Quali$FC316[i]<-"maison/ferme"
   }
  else {
    Quali$FC316[i]<-"autres_types_logements"
  }
}

for (i in 1:length(Quali$FC812)){
   if (Quali$FC812[i]==1){
     Quali$FC812[i]<-"fermier/proprio"
   }
  else {
    Quali$FC812[i]<-"locataire/loge_gratis"
  }
}

for (i in 1:length(Quali$FC9be11)){
   if (Quali$FC9be11[i]==1){
     Quali$FC9be11[i]<-"HLM"
   }
  else {
    Quali$FC9be11[i]<-"no_HLM"
  }
}

for (i in 1:length(Quali$FC9be12347)){
   if (Quali$FC9be12347[i]==1){
     Quali$FC9be12347[i]<-"entreprise_assos_autres"
   }
  else {
    Quali$FC9be12347[i]<-"no_entreprise_assos_autres"
  }
}

for (i in 1:length(Quali$FC9be156)){
   if (Quali$FC9be156[i]==1){
     Quali$FC9be156[i]<-"famille_particulier"
   }
  else {
    Quali$FC9be156[i]<-"no_famille_particulier"
  }
}

for (i in 1:length(Quali$HCU11)){
   if (Quali$HCU11[i]==1){
     Quali$HCU11[i]<-"cuisine_fermee"
   }
  else {
    Quali$HCU11[i]<-"autres_types_cuisine"
  }
}

for (i in 1:length(Quali$HCU31)){
   if (Quali$HCU31[i]==1){
     Quali$HCU31[i]<-"hotte_recycle_air"
   }
  else {
    Quali$HCU31[i]<-"no_hotte_recycle_air"
  }
}
for (i in 1:length(Quali$HCU323)){
   if (Quali$HCU323[i]==1){
     Quali$HCU323[i]<-"hotte_rejet_extr"
   }
  else {
    Quali$HCU323[i]<-"no_hotte_rejet_ext"
  }
}

for (i in 1:length(Quali$HCU34)){
   if (Quali$HCU34[i]==1){
     Quali$HCU34[i]<-"pas_hotte"
   }
  else {
    Quali$HCU34[i]<-"avec_hotte"
  }
}

for (i in 1:length(Quali$HPLBO)){
   if (Quali$HPLBO[i]==1){
     Quali$HPLBO[i]<-"plancher_pb_bois"
   }
  else {
    Quali$HPLBO[i]<-"plancher_pb_beton/autres"
  }
}
for (i in 1:length(Quali$KCC1be1089)){
   if (Quali$KCC1be1089[i]==1){
     Quali$KCC1be1089[i]<-"chauff_elec/autres"
   }
  else {
    Quali$KCC1be1089[i]<-"no_chauff_elec/autres"
  }
}
for (i in 1:length(Quali$KCC1be11)){
   if (Quali$KCC1be11[i]==1){
     Quali$KCC1be11[i]<-"chauff_fioul"
   }
  else {
    Quali$KCC1be11[i]<-"no_chauff_fioul"
  }
}
for (i in 1:length(Quali$KCC1be1234)){
   if (Quali$KCC1be1234[i]==1){
     Quali$KCC1be1234[i]<-"chauff_gaz"
   }
  else {
    Quali$KCC1be1234[i]<-"no_chauff_gaz"
  }
}

for (i in 1:length(Quali$KCC1be1567)){
   if (Quali$KCC1be1567[i]==1){
     Quali$KCC1be1567[i]<-"chauff_bois/charbon"
   }
  else {
    Quali$KCC1be1567[i]<-"no_bois/charbon"
  }
}
Quali$KCC1be1555 <-NULL

for (i in 1:length(Quali$KCC267)){
   if (Quali$KCC267[i]==1){
     Quali$KCC267[i]<-"chauff_collectif"
   }
  else {
    Quali$KCC267[i]<-"no_chauff_collectif"
  }
}

for (i in 1:length(Quali$KCC34)){
   if (Quali$KCC34[i]==1){
     Quali$KCC34[i]<-"chauff_elect"
   }
  else {
    Quali$KCC34[i]<-"no_chauff_elect"
  }
}

for (i in 1:length(Quali$KCC5)){
   if (Quali$KCC5[i]==1){
     Quali$KCC5[i]<-"chauff_indiv"
   }
  else {
    Quali$KCC5[i]<-"no_chauff_indiv"
  }
}

for (i in 1:length(Quali$KEIU1)){
   if (Quali$KEIU1[i]==1){
     Quali$KEIU1[i]<-"chauff_eau_sans_balon"
   }
  else {
    Quali$KEIU1[i]<-"no_chauff_eau_sans_balon"
  }
}

for (i in 1:length(Quali$KEIU2)){
   if (Quali$KEIU2[i]==1){
     Quali$KEIU2[i]<-"chauff_eau_avec_balon"
   }
  else {
    Quali$KEIU2[i]<-"no_chauff_eau_avec_balon"
  }
}


for (i in 1:length(Quali$KVNT2e111)){
   if (Quali$KVNT2e111[i]==1){
     Quali$KVNT2e111[i]<-"venti_méca_simple"
   }
  else {
    Quali$KVNT2e111[i]<-"no_venti_méca_simple"
  }
}

for (i in 1:length(Quali$KVNT2e112)){
   if (Quali$KVNT2e112[i]==1){
     Quali$KVNT2e112[i]<-"venti_méca_double"
   }
  else {
    Quali$KVNT2e112[i]<-"no_venti_méca_double"
  }
}


for (i in 1:length(Quali$KVNT2e12)){
   if (Quali$KVNT2e12[i]==1){
     Quali$KVNT2e12[i]<-"moteur_venti"
   }
  else {
    Quali$KVNT2e12[i]<-"no_moteur_venti"
  }
}

for (i in 1:length(Quali$KVNT2e13)){
   if (Quali$KVNT2e13[i]==1){
     Quali$KVNT2e13[i]<-"aeration_conduit/grille"
   }
  else {
    Quali$KVNT2e13[i]<-"no_aeration_conduit/grille"
  }
}

for (i in 1:length(Quali$KVNT2e14)){
   if (Quali$KVNT2e14[i]==1){
     Quali$KVNT2e14[i]<-"no_aeration"
   }
  else {
    Quali$KVNT2e14[i]<-"avec_aeration"
  }
}


for (i in 1:length(Quali$MATER017)){
   if (Quali$MATER017[i]==1){
     Quali$MATER017[i]<-"murs_princ_bois"
   }
  else {
    Quali$MATER017[i]<-"no_murs_princ_bois"
  }
}

for (i in 1:length(Quali$MATER056)){
   if (Quali$MATER056[i]==1){
     Quali$MATER056[i]<-"murs_princ_pierre"
   }
  else {
    Quali$MATER056[i]<-"no_murs_princ_pierre"
  }
}



for (i in 1:length(Quali$MATER02)){
   if (Quali$MATER02[i]==1){
     Quali$MATER02[i]<-"murs_princ_brique"
   }
  else {
    Quali$MATER02[i]<-"no_murs_princ_brique"
  }
}


for (i in 1:length(Quali$MATER03)){
   if (Quali$MATER03[i]==1){
     Quali$MATER03[i]<-"murs_princ_beton"
   }
  else {
    Quali$MATER03[i]<-"no_murs_princ_beton"
  }
}

for (i in 1:length(Quali$MATER04)){
   if (Quali$MATER04[i]==1){
     Quali$MATER04[i]<-"murs_princ_parpaing"
   }
  else {
    Quali$MATER04[i]<-"no_murs_princ_parpaing"
  }
}

for (i in 1:length(Quali$REAB1)){
   if (Quali$REAB1[i]==1){
     Quali$REAB1[i]<-"renov-5ans"
   }
  else {
    Quali$REAB1[i]<-"no_renov-5ans"
  }
}
for (i in 1:length(Quali$REAB23)){
   if (Quali$REAB23[i]==1){
     Quali$REAB23[i]<-"renov+5ans"
   }
  else {
    Quali$REAB23[i]<-"no_renov+5ans"
  }
}

for (i in 1:length(Quali$Fumeurs.FUMEURn)){
   if (Quali$Fumeurs.FUMEURn[i]==1){
     Quali$Fumeurs.FUMEURn[i]<-"aucun_fumeurs"
   }
  else {
       if (Quali$Fumeurs.FUMEURn[i]==2){
         Quali$Fumeurs.FUMEURn[i]<-"pas_de_fumeurs_iterieur"
       }
       else{
           if (Quali$Fumeurs.FUMEURn[i]==3){
             Quali$Fumeurs.FUMEURn[i]<-"un_fumeur"
           }
            else {
              Quali$Fumeurs.FUMEURn[i]<-"plus_de_un_fumeur"
              
            }
         
       }
   }
    
    
  }


for (i in 1:length(Quali$REAB4)){
   if (Quali$REAB4[i]==1){
     Quali$REAB4[i]<-"jamais_renov"
   }
  else {
    Quali$REAB4[i]<-"renov"
  }
}

for (x in 1:68){
  Quali[,x] <- as.factor(Quali[,x])

}
Quali$ACTP1 <-NULL
Quali$FC812 <-NULL
Quali$FC316 <-NULL
Quali$FC9be11 <-NULL
Quali$FC9be12347 <-NULL
Quali$FC9be156 <-NULL
Quali$KCC267 <-NULL
Quali$KCC34 <-NULL
Quali$KCC5 <-NULL
Quali$KEIU1<-NULL
logement_Quali <- Quali[,c(2:29,37)]

```
```{r, include=TRUE}

logement_Quali=as.data.frame(logement_Quali)
logement_Quanti = as.data.frame(logement_Quanti)
```


```{r}
#Creating  data for the study
study <- merge(logement_Quali, logement_Quanti, by.x = "idn.lieu", by.y ="Idn_lieu")
rownames(study) <- study$idn.lieu
study$idn.lieu<-NULL
```

```{r}
colnames(study)
```


Study of the data according to the hypothisis of the existance of different types of houses:
Doing a FAMD to analyse simulitude of houses using all types of data.

```{r}
res.famd <- FAMD(study, ncp =200, graph = TRUE)
```

Proportion of variance explained by dimensions.
```{r}
eig.val <- get_eigenvalue(res.famd)
head(eig.val)
fviz_screeplot(res.famd)
```
Contribution ; qualtyof représentation ; new coordinate's system
```{r}
var <- get_famd_var (res.famd)
# Coordonnées des variables
head(var$coord)
# Cos2: qualité de représentation
head(var$cos2)
# Contributions aux dimensions
head(var$contrib)
```

```{r}
# Graphique des variables
fviz_famd_var (res.famd, repel = TRUE)

```
Contribution aux 2 premiers axes. 
```{r}
# Contribution à la première dimension
fviz_contrib (res.famd, "var", axes = 1)
# Contribution à la deuxième dimension
fviz_contrib (res.famd, "var", axes = 2)
```
results for quanti variables 
```{r}
quanti.var <- get_famd_var(res.famd, "quanti.var")
quanti.var 
```
Corrélation circul
```{r}
fviz_famd_var(res.famd, "quanti.var", repel = TRUE,
              col.var = "black")
```
Coloration according to the cotribution
```{r}
fviz_famd_var(res.famd, "quanti.var", col.var = "contrib", 
             gradient.cols = c("#00ABBB", "#E7B700", "#FC1E07"),
             repel = TRUE)
```
Coloration according to thequality of representation 
```{r}
fviz_famd_var(res.famd, "quanti.var", col.var = "cos2",
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"), 
             repel = TRUE,select.var = list(name = NULL,cos2 = 0.25, contrib = NULL))
```
Results for quanti variables 
```{r}
quali.var <- get_famd_var(res.famd, "quali.var")
quali.var 
```

```{r}
fviz_famd_var(res.famd, "quali.var", col.var = "contrib", 
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"), select.var  = list(name = NULL,cos2 = NULL, contrib =10))
```

Individus
```{r}
ind <- get_famd_ind(res.famd)
fviz_famd_ind(res.famd, gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
             repel = TRUE)
```
Classification hérarchique 
```{r}
t = res.famd$ind$coord
res.hcpc <- HCPC (t, nb.cluster=0 ,graph = TRUE, consol=TRUE,description=FALSE)
```
```{r}
get_clust_tendency(t,n=500, graph = TRUE, gradient = list(low = "red",mid = "white", high = "blue"), seed = 123)
```

```{r}
fviz_cluster(t, geom = "point", main = "Factor map")
```
Kmeans
```{r}
set.seed(123)
km.res <- kmeans(t, 3, nstart = 25)
# 3. Visualize
library("factoextra")
fviz_cluster(km.res, data = t[,1:2],
             palette = c("#00AFBB","#2E9FDF", "#E7B800", "#FC4E07"),
             ggtheme = theme_minimal(),
             main = "Partitioning Clustering Plot",
             geom = c("point")
             )
```



```{r}
groupe1 = Polluant$Formldehyde[which(km.res$cluster[(Polluant$Idn_lieu)]==1)]
groupe2 = Polluant$Formldehyde[which(km.res$cluster[(Polluant$Idn_lieu)]==2)]
groupe3= Polluant$Formldehyde[which(km.res$cluster[(Polluant$Idn_lieu)]==3)]
hist(groupe1,breaks=20,xlab = "Formaldehyde en microgrammes/m3")
hist(groupe2,breaks=20,xlab = "Formaldehyde en microgrammes/m3")
hist(groupe3,breaks=20,xlab = "Formaldehyde en microgrammes/m3")

```

```{r}
hist(groupe1,breaks=20,xlab = "Formaldehyde en microgrammes/m3")
hist(groupe2,breaks=20,xlab = "Formaldehyde en microgrammes/m3")
hist(groupe3,breaks=20,xlab = "Formaldehyde en microgrammes/m3")
```




```{r}
summary(groupe1)
summary(groupe2)
summary(groupe3)

```

```{r}
boxplot(f1,f2,f3)

```


```{r}
groupe1bis = Polluant$benzene[which(km.res$cluster[(Polluant$Idn_lieu)]==1)]
groupe2bis = Polluant$benzene[which(km.res$cluster[(Polluant$Idn_lieu)]==2)]
groupe3bis= Polluant$benzene[which(km.res$cluster[(Polluant$Idn_lieu)]==3)]
hist(groupe1bis,breaks=20,xlab = "Benzene en microgrammes/m3")
hist(groupe2bis,breaks=20,xlab = "Benzene en microgrammes/m3")
hist(groupe3bis,breaks=20,xlab = "Benzene en microgrammes/m3")
```
#Étude formaldehyde
##Création des sous-ensembles

```{r}
t <- read.csv("~/Bureau/Etude de cas 1/t.txt")
```

```{r}
G_study= merge(t, Polluant.5[,c(1,2,6)], by.x = "Id.lieu", by.y ="Idn_lieu")

```

```{r}
G_1studyfor= subset(G_study, km.res$cluster[(G_study$Id.lieu)]==1)
G_1studyfor$benzene<-NULL
G_2studyfor= subset(G_study, km.res$cluster[(G_study$Id.lieu)]==2)
G_2studyfor$benzene<-NULL
G_3studyfor= subset(G_study, km.res$cluster[(G_study$Id.lieu)]==3)
G_3studyfor$benzene<-NULL
```
##Sélection des varaibles 
```{r}
model <- lm(G_1studyfor[,c(64)]~ ., data = G_1studyfor[,-c(1,64)])
K<-ols_step_both_p(model, details=TRUE)
```

```{r}
plot(K)
```
```{r}
model <- lm(G_2studyfor[,c(64)]~ ., data = G_2studyfor[,-c(1,64)])
K<-ols_step_both_p(model, details=TRUE)
plot(K)
```
```{r}
model <- lm(G_3studyfor[,c(64)]~ ., data = G_3studyfor[,-c(1,64)])
K<-ols_step_both_p(model, details=TRUE)
plot(K)
```
##Modèles
###SVM
```{r}
msvm1<-svm(G_1studyfor[,c(64)]~ Dim.14+ Dim.47+ Dim.13+ Dim.23 +Dim.16+Dim.52+Dim.19+Dim.38   , data=G_1studyfor[,-c(1,64)], kernel="radial",scale=T)
```
```{r}
print(msvm1)
ygrid = predict(msvm1,G_1studyfor[,-c(1,64)])
```
```{r}
t<- rmse(G_1studyfor[,c(64)],ygrid)
```



```{r}
msvm2<-svm(G_2studyfor[,c(64)]~., data=G_2studyfor[,-c(1,64)], kernel="radial",scale=T)
```
```{r}
print(msvm2)
ygrid = predict(msvm2,G_2studyfor[,-c(1,64)])
t<- rmse(G_2studyfor[,c(64)],ygrid)
print(t)
```

```{r}
msvm3<-svm(G_3studyfor[,c(64)]~., data=G_3studyfor[,-c(1,64)], kernel="polynomial",scale=T)
```
```{r}
print(msvm3)
ygrid = predict(msvm3,G_3studyfor[,-c(1,64)])
t<- rmse(G_3studyfor[,c(64)],ygrid)
print(t)
```
###Reglin
```{r}
reglin1<-lm(G_1studyfor[,c(64)]~., data=G_1studyfor[,-c(1,64)])
```
```{r}
print(reglin1)
ygrid = predict(reglin1,G_1studyfor[,-c(1,64)])
t<- rmse(G_1studyfor[,c(64)],ygrid)
print(t)
```
```{r}
reglin2<-lm(G_2studyfor[,c(64)]~., data=G_2studyfor[,-c(1,64)])
```
```{r}
print(reglin1)
ygrid = predict(reglin2,G_2studyfor[,-c(1,64)])
t<- rmse(G_2studyfor[,c(64)],ygrid)
print(t)
```

```{r}
reglin3<-lm(G_3studyfor[,c(64)]~., data=G_3studyfor[,-c(1,64)])
```
```{r}
print(reglin3)
ygrid = predict(reglin3,G_3studyfor[,-c(1,64)])
t<- rmse(G_3studyfor[,c(64)],ygrid)
print(t)
```

###Kpp
```{r}
mkpp1<-knnreg(G_1studyfor[,-c(1,64)], test = NULL, G_1studyfor[,c(64)], k = 5, use.all=T)
```
```{r}
print(mkpp1)
ygrid = predict(mkpp1,G_1studyfor[,-c(1,64)])
t<- rmse(G_1studyfor[,c(64)],ygrid)
print(t)
```
```{r}
mkpp2<-knnreg(G_2studyfor[,-c(1,64)], test = NULL, G_2studyfor[,c(64)], k = 5, use.all=T)
```
```{r}
print(mkpp2)
ygrid = predict(mkpp2,G_2studyfor[,-c(1,64)])
t<- rmse(G_2studyfor[,c(64)],ygrid)
print(t)
```
```{r}
mkpp3<-knnreg(G_3studyfor[,-c(1,64)], test = NULL, G_3studyfor[,c(64)], k = 5, use.all=T)
```
```{r}
print(mkpp3)
ygrid = predict(mkpp3,G_3studyfor[,-c(1,64)])
t<- rmse(G_3studyfor[,c(64)],ygrid)
print(t)
```


###logreg
```{r}
logreg1<-glm(G_1studyfor[,c(64)]~., data=G_1studyfor[,-c(1,64)])
```
```{r}
print(logreg1)
ygrid = predict(logreg1,G_1studyfor[,-c(1,64)])
t<- rmse(G_1studyfor[,c(64)],ygrid)
print(t)
```


```{r}
logreg2<-glm(G_2studyfor[,c(64)]~., data=G_2studyfor[,-c(1,64)])
```
```{r}
print(logreg2)
ygrid = predict(logreg2,G_2studyfor[,-c(1,64)])
t<- rmse(G_2studyfor[,c(64)],ygrid)
print(t)
```
```{r}
logreg3<-glm(G_3studyfor[,c(64)]~., data=G_3studyfor[,-c(1,64)])
```
```{r}
print(logreg3)
ygrid = predict(logreg3,G_3studyfor[,-c(1,64)])
t<- rmse(G_3studyfor[,c(64)],ygrid)
print(t)
```
